---
title: "COMPSCIX 415.2 Homework 7"
author: "Claude Phan"
date: "3/18/19"
output:
  html_document:
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My Github repository for my assignments can be found at this URL: https://github.com/claudephan/compscix-415-2-assignments.git

```{r load_packages, warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
library(ggplot2)
library(broom)
library(corrplot)
```

```{r}
df <- read.table("train.csv", header=TRUE, 
   sep=",")
```

## Exercise 1

There are 1460 observations and 81 variables.

## Exercise 2

```{r}
salePrice <- df$SalePrice

p <- ggplot(df, aes(SalePrice)) +
  geom_histogram()
p
```

Covariance between SalesPrice & Neighborhood

```{r}

c <- cov(df$SalePrice, as.numeric(df$Neighborhood))
c
```

Covariance between SalesPrice & OverallQual

```{r}

c2 <- cov(df$SalePrice, as.numeric(df$OverallQual))
c2
```


## Exercise 3

```{r}
mean_salePrice <- mean(salePrice)
sale_lm <- lm(formula = df$SalePrice ~ Id, data = df)
tidy(sale_lm)
mean_salePrice
summary(sale_lm)
```

The intercept from lm model is $183,937 vs the average SalePrice of $180,921. We have a low R-square value because there is not a strong relationship between listing ID and sale price. 


## Exercise 4

The 3 features GrLivArea, OverallQual, and Neighborhood play an important role in the value of a house. I think the relationship can be estimated linearly as the 4 variables are integers with higher values resulting in either better better quality or larger area. Neighborhood might be difficult to estimate linearly though. 


```{r}
sale_lm2 <- lm(formula = df$SalePrice ~ GrLivArea + OverallQual + Neighborhood, data = df)
tidy(sale_lm2)

```

• How would you interpret the coefficients on GrLivArea and OverallQual? 

GrLivArea and OverallQual coefficients are how much the saleprice estimate will be affected by different values of living area space and the quality rating.

• How would you interpret the coefficient on NeighborhoodBrkSide?  

The NeighborhoodBrkSide coefficient means that the sale price estimate for a unit in that neighborhood will be lowered. In relations to the other neighborhood, it is a neighborhood which lowers the value of the house. 

• Are the features significant?  

GvLivArea and OverallQual are pretty significant as they have very small p-values, however neighborhood is not so much.

• Is the model a good fit?  

The model is pretty good fit. it has a high r squared value along with a very small p-value.

```{r}
summary(sale_lm2)
```

## Exercise 6

One downside of the linear model is that it is sensitive to unusual values because the distance incorporates a squared term. Fit a linear model to the simulated data below (use y as the target and x as the feature), and look at the resulting coefficients and R-squared. Rerun it about 5-6 times to generate different simulated datasets. What do you notice about the model’s coefficient on x and the R-squared values?  

The r-square valued changes in every run. The coefficient not so much, but it is expected that R-square changes because there is more variability in the data. What this is saying is that the linear model is generally about the same each time, but how much of the data can the model properly explain each time changes based on unusual values.

```{r}
sim1a <- tibble(
x = rep(1:10, each = 3),
y = x * 1.5 + 6 + rt(length(x), df = 2)
)
```

```{r}
test_lm <- lm(formula = y ~ x , data = sim1a)
tidy(test_lm)
summary(test_lm)
```

